%%% LaTeX Template
%%% This template can be used for both articles and reports.
%%%
%%% Copyright: http://www.howtotex.com/
%%% Date: February 2011

%%% Preamble
\documentclass[paper=a4, fontsize=11pt]{scrartcl}	% Article class of KOMA-script with 11pt font and a4 format
\usepackage[margin=0.7in]{geometry}
\usepackage[english]{babel}															% English language/hyphenation
\usepackage[protrusion=true,expansion=true]{microtype}				% Better typography
\usepackage{amsmath,amsfonts,amsthm}										% Math packages
%\usepackage{color,transparent}													% If you use color and/or transparency
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption}	% Custom captions under/above floats
\usepackage{epstopdf}																	% Converts .eps to .pdf
\usepackage{subfig}																		% Subfigures
\usepackage{booktabs}																	% Nicer tables
\usepackage[pdftex]{graphicx}

%%% Advanced verbatim environment
\usepackage{verbatim}
\usepackage{fancyvrb}
\DefineShortVerb{\|}								% delimiter to display inline verbatim text


%%% Custom sectioning (sectsty package)
\usepackage{sectsty}								% Custom sectioning (see below)
\allsectionsfont{%									% Change font of al section commands
	\usefont{OT1}{bch}{b}{n}%					% bch-b-n: CharterBT-Bold font
%	\hspace{15pt}%									% Uncomment for indentation
	}

\sectionfont{%										% Change font of \section command
	\usefont{OT1}{bch}{b}{n}%					% bch-b-n: CharterBT-Bold font
	\sectionrule{0pt}{0pt}{-5pt}{0.8pt}%	% Horizontal rule below section
	}


%%% Custom headers/footers (fancyhdr package)
\usepackage{fancyhdr}
\pagestyle{fancyplain}
\fancyhead{}														% No page header
\fancyfoot[C]{\thepage}										% Pagenumbering at center of footer
\renewcommand{\headrulewidth}{0pt}				% Remove header underlines
\renewcommand{\footrulewidth}{0pt}				% Remove footer underlines
\setlength{\headheight}{13.6pt}

%%% Equation and float numbering
\numberwithin{equation}{section}															% Equationnumbering: section.eq#
\numberwithin{figure}{section}																% Figurenumbering: section.fig#
\numberwithin{table}{section}

\usepackage[parfill]{parskip}
\usepackage{float}
\usepackage{hyperref}
\usepackage[numbers]{natbib}															% Tablenumbering: section.tab#


%%% Title
\title{
	\vspace{-0.5in} 	\usefont{OT1}{bch}{b}{n}
	 Personal Statement \
}

% Authors
\author{
	\usefont{OT1}{bch}{m}{n} Samuel Jackson
%	\\ \usefont{OT1}{bch}{m}{n} University Of Aberystwyth
%	\\   \texttt{slj11@aber.ac.uk}
}
%
%\author{}
\date{}

\begin{document}
%\maketitle
\section*{Sam Jackson - Personal Statement}
My enthusiasm for computer science comes from two factors: my natural curiosity towards things I don't understand and my passion for problem solving. Computers are complex machines and I am continually fascinated by new ways in which they can be applied them to solving problems in an intelligent way. For me the most exciting part of my subject is learning a new or technique and applying it to solve problems. I want to spend my career solving challenging problems, not reinventing the wheel.

I'm interested in getting into research in medical imaging for a variety of reasons. Firstly, I think this provides a very challenging area of research which provides numerous challenges to even the most experienced researcher. Secondly I believe that medical imaging is a very active area of research with an extremely broad scope of research opportunities. Finally, I believe that medical imaging is a worth while research area because the output that it creates has direct application to the real world.

The centre for doctoral training in medical imaging caught my attention as an fantastic opportunity to get started in this research area. The thing excites me most about the CDT is the collaboration that it can offer between clinical and non-clinical experts, which I feel is one of the most important features on offer at UCL. I also feel that the fact that the programme structure includes a first year MRes. As an undergraduate applicant I feel that will give me an opportunity to get a better grounding with the technical skills necessary to complete a PhD in medical imaging.

Currently I am working through the fourth year of my degree where I am currently undertaking my dissertation project applying dimensionality reduction techniques to the feature space of both real and synthetically generated mammograms. The end goals of the project are to evaluate the similarity the two datasets under projection, particularly in regards to risk classification. I have enjoyed every second of this project so far and am eager to develop this interest further through postgraduate study.

Previously during my undergraduate I undertook a placement year at ISIS Neutron source where I worked to develop data analysis software for neutron scattering instruments where I worked in close collaboration between computer scientists and physicists. It was during this placement that I realised the importance of collaboration between disciplines and is while I feel this is an important factor in my choice of academic environment. This experience also improvement my communication skills through the requirement for constant communication members for both teams I was a involved with.

My communication skills are also emphasised by my prior experience as a practical demonstrator during my undergraduate. This was one of my most rewarding university experiences because I was given the opportunity to help pass on my passion for computer science to younger students while at the same time keeping my own technical knowledge sharp. I would hope that during the postgraduate course at UCL there would potentially an opportunity to continue to get involved in teaching.



 

%
%I'm drawn to apply to postgraduate positions in the medical domain for a number of factors. Firstly, the area has a clear and meaningful application towards help people which makes it personally satisfying and a worthwhile endeavour. Secondly, I enjoy the idea of working in a areas on the borders of disciplines. During my undergraduate I took an industrial year out at ISIS Neutron Source where I worked in close collaboration with computer scientists and physicists on neutron scattering analysis software. I found that one of the most rewarding parts of the job was working alongside people from a completely different scientific discipline. Thirdly, I believe that the problems posed in medical analysis offer some of the most challenging problems and is an exciting an active research area in which my academic ambitions can be realised.
%
%Currently, I am working through the fourth year of my degree and undertaking a dissertation project looking into the application of dimensionality reduction techniques to the feature space of both real and synthetically generated mammograms. The end goals of the project are to try and understand the similarity the two datasets under projection, particularly in regards to risk classification. I have thoroughly enjoyed every second of this project so far and am eager to find a way to develop this interest into a potential career path.
%
%The advertised position at Wolfson Institute at the Queen Mary University of London caught my eye because of their renowned medical department.
%
%My undergraduate and placement year has given me excellent programming abilities and problem solving skills suitable to a role



\end{document}
